School closures and consolidations: the active travel and emission implications of reduced accessibility

### 2024-05-10 paper/Manuscript.qmd
Added declarations to manuscript (upon request by editorial office) and updated lock.file

>>>>

# Declarations

**Ethical approval**
Not applicable

**Participate consent**
Not applicable

**Competing interests**
The authors declare there are no personal or financial conflicts of interest.

**Authors' contributions**
A.S., A.P., C.D.H., and M.M. all contributed to the study conception and design. Material preparation, data collection
and formal analysis were performed by A.S., A.P, and C.D.H. All visuals and the first draft of the manuscript was written by A.S. A.S., A.P., C.D.H., and M.M. commented on earlier versions of the manuscript. A.S., A.P., C.D.H., and M.M.  reviewed the final manuscript.

**Funding declaration**
This work was supported by the Mobilizing Justice Partnership and the Canada Graduate Scholarships—Doctoral Program from the Social Sciences and Humanities Research Council of Canada (SSHRC).

**Availability of data and materials**
The manuscript text, code, analysis and data supporting this work is available in the lead author's GitHub repository : https://github.com/soukhova/School-closures-accessibility-impacts

### 2024-05-10 paper/Manuscript.tex
Added declarations to manuscript (upon request by editorial office) and updated lock.file

>>>>

\section{Declarations}\label{declarations}

\textbf{Ethical approval} Not applicable

\textbf{Participate consent} Not applicable

\textbf{Competing interests} The authors declare there are no personal
or financial conflicts of interest.

\textbf{Authors' contributions} A.S., A.P., C.D.H., and M.M. all
contributed to the study conception and design. Material preparation,
data collection and formal analysis were performed by A.S., A.P, and
C.D.H. All visuals and the first draft of the manuscript was written by
A.S. A.S., A.P., C.D.H., and M.M. commented on earlier versions of the
manuscript. A.S., A.P., C.D.H., and M.M. reviewed the final manuscript.

\textbf{Funding declaration} This work was supported by the Mobilizing
Justice Partnership and the Canada Graduate Scholarships---Doctoral
Program from the Social Sciences and Humanities Research Council of
Canada (SSHRC).

\textbf{Availability of data and materials} The manuscript text, code,
analysis and data supporting this work is available in the lead author's
GitHub repository :
https://github.com/soukhova/School-closures-accessibility-impacts
